PANCHANGE_data_preprocessing

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
NBR MHD finished. Adding eating disorders cleaning section to account for routing logic. Verified mhd section all ran properly.

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(tidyverse)
library(eeptools) #Needed to calculate age from birthdate
```

@@

nbr.employment.raw.id <- nbr.employment.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(nbr.employment.raw.id)
# Inspect colnames
colnames(nbr.employment.raw.id)
#Differences
dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
}
```

@@

## Highest education (baseline)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

Check highest education coding
```{r Highest education check}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.phd_numeric,
         employment.masters_degree_or_equivalent_numeric,
         employment.postgraduate_degree_or_equivalent_numeric,
         employment.bachelors_degree_or_equivalent_numeric,
         employment.a_levelsas_levels_or_equivalent_numeric,
         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
         employment.o_levelsgcses_or_equivalent_numeric,
         employment.cses_or_equivalent_numeric
  )
}
```

@@

# glad gad

```{r glad gad cols}
if(GLAD == TRUE){
glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
dim(glad.gad.raw)
colnames(glad.gad.raw)
}
```

```{r glad gad cleaning}
if(GLAD ==TRUE){
exclude_cols <- c("Sample",
                  "ID")
glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad copy gad}
if(GLAD == TRUE){
prepan.gad.raw.id <- glad.gad.raw.id
}
```

```{r edgi gad cols}
if(EDGI == TRUE){
  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
  dim(edgi.gad.raw)
  colnames(edgi.gad.raw)
}
```

```{r edgi gad cleaning}
if(EDGI == TRUE){
exclude_cols <- c("Sample",
                  "ID")

@@

```{r nbr copy gad}
if(EDGI == TRUE){
  prepan.gad.raw.id <- edgi.gad.raw.id
}
```

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Rename columns that differ from GLAD
nbr.mhd.raw.id_renamed <- nbr.mhd.raw.id %>% 
  mutate(
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric
    ) %>% 
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR dooesn't ask about schizoaffective
    mhd.schizoaffective_disorder_numeric = NA
  )

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "2" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

@@

Eating disorders group
```{r mhd eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r mhd psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

@@

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r mhd bipolar_and_schizophrenia_numeric}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
      )
  )

@@

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

```{r glad mhd personality_cluster_b}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

Control grouping
These individuals have no self report diagnosis of any kind that we measure. 
Controls = 784
```{r glad mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

```{r glad mhd summary}
summarytools::dfSummary(
  mhd.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

>>>>

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
#library(psych)
library(tidyverse)
library(eeptools) #Needed to calculate age from birthdate
```

@@

nbr.employment.raw.id <- nbr.employment.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  #mutate(
  #  ID = as.numeric(ID) ##NBR IDs have a letter at the end so can't be coerced to numeric
  #  ) %>% 
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(nbr.employment.raw.id)
# Inspect colnames
colnames(nbr.employment.raw.id)
#Differences
dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
head(nbr.employment.raw.id
     )
}
```

@@

## Highest education (baseline)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

Check highest education coding
```{r Highest education check}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.phd_numeric,
         employment.masters_degree_or_equivalent_numeric,
         employment.postgraduate_degree_or_equivalent_numeric,
         employment.bachelors_degree_or_equivalent_numeric,
         employment.a_levelsas_levels_or_equivalent_numeric,
         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
         employment.o_levelsgcses_or_equivalent_numeric,
         employment.cses_or_equivalent_numeric
  )
}
```

@@

# glad gad (prepan)

```{r glad gad prepan cols}
if(GLAD == TRUE){
glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
dim(glad.gad.raw)
colnames(glad.gad.raw)
}
```

```{r glad gad prepan cleaning}
if(GLAD ==TRUE){
exclude_cols <- c("Sample",
                  "ID")
glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad copy prepan gad}
if(GLAD == TRUE){
prepan.gad.raw.id <- glad.gad.raw.id
}
```

```{r edgi gad prepan cols}
if(EDGI == TRUE){
  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
  dim(edgi.gad.raw)
  colnames(edgi.gad.raw)
}
```

```{r edgi gad prepan cleaning}
if(EDGI == TRUE){
exclude_cols <- c("Sample",
                  "ID")

@@

```{r edgi copy prepan gad}
if(EDGI == TRUE){
  prepan.gad.raw.id <- edgi.gad.raw.id
}
```

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(#ID = as.numeric(ID), ## NBR IDs end with letters so can't be numeric
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Rename columns that differ from GLAD
nbr.mhd.raw.id_renamed <- nbr.mhd.raw.id %>% 
  mutate(
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric
    ) %>% 
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective
    mhd.schizoaffective_disorder_numeric = NA
  )

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "3" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

@@

Eating disorders group

```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_numeric == "1" ~ 1),
    mhd.psychological_overeating_or_bingeeating_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.psychological_overeating_or_bingeeating_numeric == "0" ~ 0,
                mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1)
    )
}

```{r mhd eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r mhd psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
        )
    )

@@

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r mhd bipolar_and_schizophrenia_numeric}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3
      )
  )

@@

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

```{r mhd personality_cluster_b}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

Control grouping
These individuals have no self report diagnosis of any kind that we measure. 
```{r mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

```{r mhd summary}
summarytools::dfSummary(
  mhd.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```
